Recommendation Generation for Performance Improvement by using Cross-Organizational Process Mining

### 2015-09-07 4_methodology/methodology.tex
no message

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{4_methodology/process-model-mining-blackbox}
  \caption{Process Model Mining Stage as Black-box }
  \label{fig:process-model-mining-blackbox}
\end{figure}

@@

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{4_methodology/process-model-mining-blackbox}
  \caption{Process Model Mining Stage as Black-box }
  \label{fig:process-model-mining-blackbox}
\end{figure}

@@

\subsubsection{Replay and Performance Indicator Calculation}
\label{subsubsec:replay-and-performance-summary}
Replay of event logs on process models is based on the idea of \textit{alignment} which is formalized in \cite{van2012replaying} and the basic assumption in this concept is that process models and event logs have the same activity labels. Alignment is based on \textit{moves in the model and log} and in order to have a successful replay where optimal alignment should be achieved. As proposed in \cite{adriansyah2011conformance, adriansyah2011towards}, $A^{*}$ algorithm which is a path-finding algorithm based on graphs is used to find optimal alignment of event logs on the process models. With the generated and user-specified inputs, replay and performance indicator calculation in the methodology can be visualized in Figure~\ref{fig:replay-and-performance-indicator-calculation}. For each organization, the steps in the diagram are followed with the corresponding event logs and process models; and the resulting process summaries are used for further analysis.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{4_methodology/replay-and-performance-indicator-calculation}
  \caption{Replay and Performance Indicator Calculation Stage as Black-box}
  \label{fig:replay-and-performance-indicator-calculation}
\end{figure}

\subsubsection{Performance Indicator Clustering}
\label{subsubsec:performance-indicator-clustering}

Clustering is based on the idea of collecting the set of observations into clusters so that observations within the same cluster are similar whereas the observations from different clusters are dissimilar. In this thesis study, clustering is used to gather organizations based on their performance indicator data. In this study, a generic approach based on centroid-based clustering is exploited. For the fixed number of \textit{k} clusters, the approach is well-known as \textit{k-means clustering}. Considering the popularity of this approach and its extensions, random initialization based \textit{k-means++} approach from the study of Arthur and Vassilvitskii \cite{arthur2007} is used to cluster organizations. For each organization, \textit{Performance Summary} data is used as the data source in clustering. Since number of clusters are not known priori, k-means clustering is applied starting \textit{k} from 1 to the number of organizations. For each clustering with different number of clusters, SSE values are plotted and user is made to select the appropriate cluster size. For the selected cluster size, clustering related information is used to generate recommendations in the further steps. This stage of methodology can be visualized as an input-output system in Figure~\ref{fig:performance-indicator-clustering-blackbox}. 
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{4_methodology/performance-indicator-clustering-blackbox}
  \caption{Performance Indicator Clustering Stage as Black-box }
  \label{fig:performance-indicator-clustering-blackbox}
\end{figure}
